Parameter Recovery Validation

### 2025-06-15 nbs/concepts/parameter-recovery-validation/index.qmd
docs(parameter-recovery-validation): fix notation in model development overview
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

- **Time coordinates**: Independent latent $t^*_j$ coordinates sampled uniformly within process duration $T_{\max}$
- **Dynamics**: Piecewise constant transcription with three phases (off, on, return-to-off)
- **Parameters**: $\gamma^*_i$, $R_{\text{on},i}$ (fold-change), $t^*_{0,\text{on}i}$ (onset), $\delta^*_i$ (duration), with independent temporal structure
- **Key innovation**: Fixed reference state ($\alpha^*_{\text{off}i} = 1.0$) eliminates parameter redundancy
- **Enhanced patterns**: Supports pre-activation scenarios with negative onset times
- **Analytical solutions**: Closed-form solutions for all three phases, including $\gamma^*_i = 1$ special case
- **Biological realism**: Steady-state initial conditions and rich expression pattern representation
- **Observation Model**: Same Poisson scaling with characteristic scales and capture efficiency
- **Likelihood**: Poisson

>>>>

- **Time coordinates**: Independent latent $t^*_j$ coordinates sampled uniformly within process duration $T_M$
- **Dynamics**: Piecewise constant transcription with three phases (off, on, return-to-off)
- **Parameters**: $\gamma^*_i$, $R_{\text{on},i}$ (fold-change), $t^*_{on,i}$ (onset), $\delta^*_i$ (duration), with independent temporal structure
- **Key innovation**: Fixed reference state ($\alpha^*_{\text{off}i} = 1.0$) eliminates parameter redundancy
- **Enhanced patterns**: Supports pre-activation scenarios with negative onset times
- **Analytical solutions**: Closed-form solutions for all three phases, including $\gamma^*_i = 1$ special case
- **Biological realism**: Steady-state initial conditions and rich expression pattern representation
- **Observation Model**: Same Poisson scaling with characteristic scales and capture efficiency
- **Likelihood**: Poisson
